Downloading data

### 2023-05-15 episodes/downloading-data.Rmd
Complete draft of quality control

Use the `mkdir` command to make the following directories:  
dc\_workshop  
dc\_workshop/docs  
dc\_workshop/data  
dc\_workshop/results

@@

Let's download data for two *M. tuberculosis* genomes with a for loop

@@

This will run over night. We will therefore detach the session to work further.

>>>>

Use the `mkdir` command to make the following directories:  
molepi
molepi/docs  
molepi/data  
molepi/results

@@

Let's download data for two *M. tuberculosis* genomes with a `for` loop. Here is an example, but you may choose two other samples (see below).

@@

This will run for a while (maybe 5 minutes).
